Plots and tables summarizing results of Poisson simulations

### 2020-06-26 analysis/poisson.Rmd
Added example run of smash and HF methods to poisson demo.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
theme_set(theme_cowplot())
```

@@

This plot shows the function used to simulate the "Spikes" data sets
at the $(1/100, 3)$ intensity range, along with an example data set
(black circles):

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x <- rpois(n,mu.s)
p1 <- create.signal.plot(t,x,mu.s)
print(p1)
```

>>>>

```{r load-pkgs, message=FALSE, warning=FALSE}
library(smashr)
library(haarfisz)
library(plyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
theme_set(theme_cowplot())
```

@@

This plot shows the function used to simulate the "Spikes" data sets
at the $(1/100, 3)$ intensity range, along with an example data set
(black circles), and example fitted curves produced by the SMASH and
Haar-Fisz methods:

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s      <- 0.01 + spike.f(t)
x         <- rpois(n,mu.s)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p1 <- create.signal.plot(t,x,mu.s) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p1)
```
